### 2023-02-08 main.qmd
Initialize Quarto book

---
title             : "Gender differences in infant mental rotation"
shorttitle        : "Infant mental rotation"

author:
  - name          : "Alexander Enge"
    affiliation   : "1,2"
    corresponding : "yes"
    address       : "Stephanstraße 1a, 04103 Leipzig, Germany"
    email         : "enge@cbs.mpg.de"
  - name          : "Shreya Kapoor"
    affiliation   : "1"
  - name          : "Anne-Sophie Kieslinger"
    affiliation   : "1"
  - name          : "Michael A. Skeide"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany"
  - id            : "2"
    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"

authornote: |
  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}

  \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}

  \addORCIDlink{Anne-Sophie Kieslinger}{0000-0001-9240-4077}

  The data and code necessary to reproduce the analyses presented here are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).

  M.A.S. was supported by the German Research Foundation (DFG Grants 433715509 and 433758790), the European Research Council (ERC Starting Grant 850752), and a Jacobs Foundation Research Scholarship. A.E. was supported by a PhD scholarship from the German Academic Scholarship Foundation (Studienstiftung des deutschen Volkes).

  The authors declare that they have no conflicts of interest to disclose.

bibliography      : "manuscript_files/references.bib"
csl               : "manuscript_files/apa.csl"

appendix          : "supplement.Rmd"

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"
output            : "papaja::apa6_pdf"

header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{lineno}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{belowskip=20pt,labelfont=bf,labelsep=period,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=period,textfont=normalfont}
---

```{r, setup, include=FALSE}
# Load packages
library(papaja)
library(here)
library(readxl)
library(scales)
library(tidyverse)
library(furrr)
library(metafor)
library(brms)
library(tidybayes)
library(cowplot)

@@

# Global chunk options
knitr::opts_chunk$set(
  include = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.height = 10,
  fig.pos = "tp",
  fig.width = 7.5,
  out.width = "100%",
  warning = FALSE
)

@@

# Directory paths
data_dir <- here("data")
models_dir <- here("results/models")
figures_dir <- here("results/figures")
tables_dir <- here("results/tables")

# Read the relevant spreadsheets
raw_screen <- read_tsv(here(data_dir, "02_screen.tsv"), na = "NA")
raw_meta <- read_tsv(here(data_dir, "03_meta.tsv"), na = "NA")
raw_gender <- read_tsv(here(data_dir, "04_gender.tsv"), na = "NA")

# Add columns to the table of experiments for the meta-analysis
raw_meta %>%
  mutate(

@@

    # Combine gender and task into one column for plotting
    gender_task = factor(
      str_c(gender, task, sep = ", "),
      levels = c(
        "Female, Habituation",
        "Male, Habituation",
        "Mixed, Habituation",
        "Mixed, VoE"
      )
    )
  ) %>%
  # Order rows by experiment ID
  arrange(experiment) -> dat_all

# Get an overview of the different effect sizes
dat_all %>%
  select(
    article,
    group,
    gender_split,
    gi,
    di,
    di_type,
    d,
    d_z_t,
    d_z_f,
    d_z_diff,
    d_av,
    d_nov_pref
  ) %>%
  print(n = Inf)

# Compute standard errors of the effect sizes based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# You'll find a sensitivity analysis for `r_assumed` in the `supplement.Rmd`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) -> dat_meta_all

# Show number of experiments per gender grouping strategy (mixed/split)
table(dat_meta_all$gender_split)

@@

# We go ahead with the last solution (i.e., prefer split experiments) as to use
# the maximum amount of information while not biasing the gender results
dat_meta <- dat_both_split

# Extract some descriptive statistics so we can paste them in the main text
descriptives <- list(
  n_articles = length(unique(dat_meta$article)),
  n_experiments = nrow(dat_meta),
  n_infants = sum(dat_meta$sample_size),
  percent_female = mean(dat_meta$female_percent, na.rm = TRUE),
  min_age_months = as.integer(min(dat_meta$age_min, na.rm = TRUE) / 30.417),
  max_age_months = as.integer(max(dat_meta$age_max, na.rm = TRUE) / 30.417),
  mean_age_weighted = print_days_months(
    sum(dat_meta$age_mean * dat_meta$ni) / (sum(dat_meta$ni)),
    long = TRUE
  ),
  n_experiments_habituation = nrow(filter(dat_meta, task == "Habituation")),
  n_experiments_voe = nrow(filter(dat_meta, task == "VoE"))
)
```

\setcounter{page}{1}
\resetlinenumber

# Gender differences in infant mental rotation

\bigskip

# Research highlights

* We analyzed effect sizes of 59 mental rotation experiments including 1,798 infants

* Looking time reveals that 3–16-months-old infants are able to perform mental rotation

* Mental rotation is more reliable in male infants compared to female infants

# Abstract

Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning, and educational achievement [@shepard1971; @hegarty1999; @johnson2005]. On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013]. When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a]. Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3--16 months. We robustly found that male infants recognized rotated objects more reliably than female infants. These findings indicate that gender differences in mental rotation are already present in the first months of life.

*Keywords*: mental rotation; spatial cognition; spatial ability; infants; gender; meta-analysis

\newpage

# Introduction

The cognitive ability to move visual object representations in mind for recognition across different orientations, known as mental rotation, emerges in the first three months of life [@moore2020; @johnson2020]. Mental rotation is a key component of intelligence and a powerful predictor of learning outcome and educational achievement [@shepard1971; @hegarty1999; @johnson2005].

Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average [@linn1985; @voyer1995; @voyer2011; @maeda2013]. Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$). Interestingly, a recent meta-analysis in 3--17-year-old children and adolescents suggests only a small-to-medium difference [mean weighted $g = 0.39$\; @lauer2019a]. Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.

In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks performed by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`\; Supplementary Table\ \@ref(tab:tabs1)) [@rochat1996; @hespos1997; @moore2008; @quinn2008; @moore2011; @frick2013b; @mohring2013; @schwarzer2013; @schwarzer2013a; @frick2014b; @quinn2014; @lauer2015; @antrilli2016; @christodoulou2016; @constantinescu2018; @erdmann2018; @gerhard2018; @slone2018; @kaaz2020; @gerhard-samunda2021; @kelch2021]. All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation` experiments) or violation of expectation experiments (`r descriptives$n_experiments_voe` experiments) [@fantz1964; @baillargeon1985]. These experiments comprised real world stimuli [e.g., toy objects\; @antrilli2016], three-dimensional digital stimuli [e.g., cube figures\; @moore2008], or two-dimensional digital stimuli [e.g., digits\; @quinn2008]. In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object or with the familiar object at a new angle. Longer looking times at the mirror image were taken as evidence that an infant still recognized the familiar object after rotation through the new orientation. In violation of expectation experiments, infants were habituated to an object that was revolving repeatedly through a certain angle. Then, either the familiar object or an unseen object was shown while they were revolving through a certain angle. Subsequently, the object disappeared behind an occluder. Finally, the occluder was removed and either the object or its mirror object were shown. Larger differences in looking times for the familiar object versus the unseen mirror image (at the new angle) were taken as evidence that an infant still recognized the familiar object after rotation through the new angle. In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.

Following previous work in older populations, we hypothesized that looking time differences in mental rotation experiments are on average longer in male compared to female infants. Effect sizes were assumed to be small.

```{r, meta}
# Specify priors
prior_meta <- c(
  set_prior("normal(0, 1)", class = "b"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

# Run prior predictive simulation
dir.create(models_dir, showWarnings = FALSE, recursive = TRUE)
brms_file_refit <- ifelse(run$bayesian_models, "always", "never")
res_prior_meta <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat_meta,
  prior = prior_meta,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_meta"),
  file_refit = brms_file_refit
)
summary(res_prior_meta)

# Run Bayesian multilevel model
res_meta <- update(
  res_prior_meta,
  sample_prior = FALSE,
  seed = seed,
  file = here(models_dir, "res_meta"),
  file_refit = brms_file_refit
)
summary(res_meta)

# Get posterior probability mass > 0 for the meta-analytic effect
(hyp_meta <- hypothesis(res_meta, "Intercept > 0")$hypothesis)

# Extract posterior draws for the meta-analytic effects
spread_draws(res_meta, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
  # Compute variances and ICC from standard deviations
  mutate(
    intercept = b_Intercept,
    sigma_article = sd_article__Intercept,
    sigma_experiment = `sd_article:experiment__Intercept`,
    sigma2_article = sigma_article^2,
    sigma2_experiment = sigma_experiment^2,
    sigma2_total = sigma2_article + sigma2_experiment,
    icc = sigma2_article / sigma2_total,
    .keep = "unused"
  ) -> draws_meta

# Summarize as means and 95% credible intervals
(summ_meta <- as.list(mean_qi(draws_meta)))
```

```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
# Get posterior draws for the effect *in each experiment*
epred_draws_meta <- epred_draws(res_meta, dat_meta, ndraws = NULL) %>%
  mutate(experiment_f = factor(experiment))

# Create forest plot
dat_meta %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment (row) per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals for each experiment
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian credible intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_meta,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_meta,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_meta$intercept),
      print_num(summ_meta$intercept.lower),
      print_num(summ_meta$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add column headers
  annotate(
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = descriptives$n_experiments + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = descriptives$n_experiments + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "2.5%",
      "97.5%"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, descriptives$n_experiments + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

# Save the plot
dir.create(figures_dir, showWarnings = FALSE)
ggsave(here(figures_dir, "fig1_meta.pdf"), width = 12, height = 14)
```

(ref:fig1-caption) **Mental rotation performance.** A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants. White squares depict the effect sizes (Hedges' $g$) for infants' mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals. Gray bars indicate the 50% and 95% credible intervals (CrI) from the Bayesian model, which take into account that experiments with smaller sample sizes or more extreme effect sizes provide less reliable information. The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).

# Results

## Mental rotation performance

For our first meta-analytic model, effect sizes were quantified as the standardized mean difference in infants' looking times for novel and familiar rotated objects. Using this effect size index, we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation. Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Figure\ \@ref(fig:fig1)). The probability for this effect being greater than zero was `r print_prob(hyp_meta$Post.Prob)`. The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level. Therefore, `r print_perc(1 - summ_meta$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_meta$icc)` was attributable to differences *between* articles.

## Effects of gender, age, and task type

```{r, reg}
# Set numerical contrasts for factor variables
contrasts(dat_meta$gender) <- MASS::contr.sdif(3)
contrasts(dat_meta$task) <- MASS::contr.sdif(2)

# Run prior predictive simulation
res_prior_reg <- brm(
  gi | se(sei) ~ 0 + Intercept + gender * age_c + task +
    (1 | article / experiment),
  data = dat_meta,
  prior = prior_reg,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_reg"),
  file_refit = brms_file_refit
)
summary(res_prior_reg)

# Run Bayesian multilevel model
res_reg <- update(
  res_prior_reg,
  sample_prior = FALSE,
  seed = seed,
  file = here(models_dir, "res_reg"),
  file_refit = brms_file_refit
)
summary(res_reg)

# Get posterior probability mass > 0 for all regression weights
(hyps_brm_reg <- list(
  intercept = hypothesis(res_reg, "Intercept > 0")$hypothesis,
  female_mixed = hypothesis(res_reg, "gender2M1 < 0")$hypothesis,
  male_female = hypothesis(res_reg, "gender3M2 > 0")$hypothesis,
  age = hypothesis(res_reg, "age_c > 0")$hypothesis,
  voe_habituation = hypothesis(res_reg, "task2M1 > 0")$hypothesis,
  female_mixed_age = hypothesis(res_reg, "gender2M1:age_c > 0")$hypothesis,
  male_female_age = hypothesis(res_reg, "gender3M2:age_c > 0")$hypothesis
))

# Extract posterior draws for the meta-analytic effects
spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
  # Compute variances and ICC from standard deviations
  mutate(
    intercept = b_Intercept,
    female_mixed = b_gender2M1,
    male_female = b_gender3M2,
    age = b_age_c,
    voe_habituation = b_task2M1,
    female_mixed_age = `b_gender2M1:age_c`,
    male_female_age = `b_gender3M2:age_c`,
    sigma_article = sd_article__Intercept,
    sigma_experiment = `sd_article:experiment__Intercept`,
    sigma2_article = sd_article__Intercept^2,
    sigma2_experiment = `sd_article:experiment__Intercept`^2,
    sigma2_total = sigma2_article + sigma2_experiment,
    icc = sigma2_article / sigma2_total,
  ) -> draws_reg

# Summarize as means and 95% credible intervals
(summ_reg <- as.list(mean_qi(draws_reg)))
```

As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Figure\ \@ref(fig:fig2)). Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_reg$male_female`$ (where $b = \Delta{g}$), 95% CrI [`r summ_reg$male_female.lower`, `r summ_reg$male_female.upper`]. The probability for this effect being larger than zero was `r print_prob(hyps_brm_reg$male_female$Post.Prob)`. We found no difference between mixed-gender and all-female samples, $b = `r -summ_reg$female_mixed`$, 95% CrI [`r -summ_reg$female_mixed.lower`, `r -summ_reg$female_mixed.upper`] (`r print_prob(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero). Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_reg$age`$, 95% CrI [`r summ_reg$age.lower`, `r summ_reg$age.upper`]. We also did not detect an interaction between gender and age ([females - mixed] $\times$ age: $b = `r summ_reg$female_mixed_age`$, 95% CrI [`r summ_reg$female_mixed_age.lower`, `r summ_reg$female_mixed_age.upper`]; [males - females] $\times$ age: $b = `r summ_reg$male_female_age`$, 95% CrI [`r summ_reg$male_female_age.lower`, `r summ_reg$male_female_age.upper`]). Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_reg$voe_habituation`$, 95% CrI [`r summ_reg$voe_habituation.lower`, `r summ_reg$voe_habituation.upper`]. The probability for this effect being greater than zero was `r print_prob(hyps_brm_reg$voe_habituation$Post.Prob)`.

```{r, fig2, include=TRUE, fig.height=5, fig.width=12, fig.cap="(ref:fig2-caption)"}
# Get draws from the posterior distribution *for each experiment*
epred_draws_reg <- epred_draws(
  res_reg,
  dat_meta,
  ndraws = NULL,
  re_formula = NA
)

# Create regression plot
dat_meta %>%
  ggplot(aes(x = age * 12, y = gi)) +
  geom_hline(yintercept = seq(-1, 2, 0.5), color = "grey90") +
  annotate(
    "rect",
    xmin = 5.5, xmax = Inf, ymin = 1.25, ymax = Inf,
    color = NA, fill = "white"
  ) +
  # Regression lines and CrIs for Habituation tasks
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = epred_draws_reg,
    alpha = .4,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95)
  ) +
  # Individual study effect sizes for Habituation tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = plot_reg_colors$habituation,
    breaks = names(plot_reg_colors$habituation),
    labels = c("Females", "Males", "Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(
    title = "Habituation tasks",
    override.aes = list(fill = NA),
    order = 1
  )) +
  # Regression lines and CrIs for VoE tasks
  ggnewscale::new_scale_color() +
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = epred_draws_reg,
    fill = NA,
    alpha = .4,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95)
  ) +
  # Individual study effect sizes for VoE tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = plot_reg_colors$voe,
    breaks = names(plot_reg_colors$voe),
    labels = c("Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(title = "VoE tasks", order = 2)) +
  # Styling
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
  scale_fill_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    fill = "CrI level",
    size = "Sample size"
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    legend.direction = "vertical",
    legend.key = element_blank(),
    legend.position = "none",
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica", color = "black")
  ) -> plot_reg

# Plot posterior distributions of the regression coefficients
epred_draws_reg_coef <- tidy_draws(res_reg)
epred_draws_reg_coef %>%
  # Convert to long format
  select(all_of(names(coef_colnames))) %>%
  gather() %>%
  mutate(coef = factor(key, levels = names(coef_colnames))) %>%
  # Plot coefficients as "half eyes" (mean + CrIs + distribution)
  ggplot(aes(x = value, y = fct_rev(coef))) +
  geom_vline(xintercept = seq(-1, 1, 0.5), color = "grey90") +
  stat_halfeye(point_interval = "mean_qi", .width = c(0.5, 0.95)) +
  # Styling
  coord_cartesian(xlim = c(-1.25, 1.25), clip = "off") +
  scale_x_continuous(breaks = seq(-1, 1, 0.5)) +
  scale_y_discrete(labels = coef_colnames) +
  labs(x = expression("Regression weight (" * Delta * italic("g") * ")")) +
  annotate(
    "text",
    label = "Fixed effects", x = -3.175, y = 7.86, hjust = 0,
    family = "Helvetica", fontface = "bold", color = "black"
  ) +
  theme_minimal() +
  theme(
    axis.line.x = element_line(colour = "black"),
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_text(
      family = "Helvetica", color = "black", size = 3.88 * .pt,
      hjust = 0, vjust = -0.1, margin = margin(l = 20)
    ),
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica", color = "black")
  ) -> plot_coef

# Save plot
ggsave(here(figures_dir, "fig2_reg.pdf"), width = 12, height = 5)
```

(ref:fig2-caption) **Effects of gender, age, and task.** (A) Squares show the effect size (Hedges' $g$) for infants' mental rotation performance in each of the 59 individual experiments. Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample; yellow = habituation task, all-male sample; red = habituation task, mixed-gender sample; purple = violation of expectation [VoE] task, mixed-gender sample). Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 50% and 95% credible interval (CrI). (B) Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 50% CrI (thick black lines) and 95% CrI (thin black lines). Gray curves indicate the posterior distribution for each effect.

```{r, gender}
# Compute relevant effect sizes for the meta-analysis of gender differences
raw_gender %>%
  # Remove effect sizes from experiments with redundant samples
  filter(!redundant) %>%
  # Add columns
  mutate(

@@

    # Compute standard error of Cohen's d, using harmonic mean of sample sizes
    ni = female_n + male_n,
    nhi = 2 / (1 / female_n + 1 / male_n),
    vi = (df / (df - 2)) * (2 / nhi) * (1 + gi^2 * (nhi / 2)) - (gi^2 / (j^2)),
    sei = sqrt(vi)
  ) %>%
  # Remove experiments that didn't provide any effect size
  filter(!is.na(gi)) -> dat_gender

# Get an overview of the different effect sizes
dat_gender %>%
  select(
    article,
    group,
    gi,
    di,
    di_type,
    d,
    d_t,
    d_f,
    d_diff,
    sei
  ) %>%
  print(n = Inf)

# Use the same priors as for the main meta-analysis
prior_gender <- prior_meta

# Run prior predictive simulation
res_prior_gender <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat_gender,
  prior = prior_gender,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_gender"),
  file_refit = brms_file_refit
)
summary(res_prior_gender)

# Run Bayesian multilevel model
res_gender <- update(
  res_prior_gender,
  sample_prior = FALSE,
  seed = seed,
  file = here(models_dir, "res_gender"),
  file_refit = brms_file_refit
)
summary(res_gender)

# Get posterior probability mass > 0 for the meta-analytic effect
(hyp_gender <- hypothesis(res_gender, "Intercept > 0")$hypothesis)

>>>>

# Main text

## Setup

```{r, message=FALSE}
# Load packages
library(papaja)
library(here)
library(scales)
library(tidyverse)
library(furrr)
library(metafor)
library(brms)
library(tidybayes)
library(cowplot)

@@

@@

# Directory paths
data_dir <- here("data")
results_dir <- here("results")
models_dir <- here(results_dir, "models")
figures_dir <- here(results_dir, "figures")
tables_dir <- here(results_dir, "tables")
```

## Introduction / Methods

### Protocol

#### PRISMA flowchart (Figure 1)

![PRISMA flowchart](results/figures/fig1_flowchart.png)

### Selection process

#### Percent agreement for binary decision (include vs. exclude)

```{r}
# Read the raw data from the screening process
raw_screen <- read_tsv(here(data_dir, "02_screen.tsv"), na = "NA")

# Percent agreement for binary decision (include vs. exclude)
with(raw_screen, mean(bin_1 == bin_2))
```

#### Cohen's $\kappa_w$ (weighted kappa)

```{r}
# Cohen's kappa
with(raw_screen, psych::cohen.kappa(cbind(bin_1, bin_2)))
```

#### Percent agreement for specific exclusion criteria

```{r}
# Compute interrater agreement for specific exclusion codes
with(raw_screen, mean(code_1 == code_2))
```

#### Cohen's $\kappa_w$ (weighted kappa)

```{r}
with(raw_screen, psych::cohen.kappa(cbind(code_1, code_2)))
```

### Effect measures

#### Conversion of effect sizes for mental rotation performance

```{r}
# Read raw data for the meta-analysis of mental rotation performance
raw_meta <- read_tsv(here(data_dir, "03_meta.tsv"), na = "NA")

# Add columns to the table of experiments
dat_all <- raw_meta %>%
  mutate(

@@

    # Combine gender and task into one column for plotting
    gender_task = factor(
      str_c(gender, task, sep = ", "),
      levels = c(
        "Female, Habituation",
        "Male, Habituation",
        "Mixed, Habituation",
        "Mixed, VoE"
      )
    )
  ) %>%
  # Order rows by experiment ID
  arrange(experiment)

# Compute standard errors of the effect sizes based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# You'll find a sensitivity analysis for `r_assumed` in the `supplement.Rmd`
r_assumed <- 0.5
dat_meta_all <- dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi))

@@

# We go ahead with the last solution (i.e., prefer split experiments) as to use
# the maximum amount of information while not biasing the gender results
dat_meta <- dat_both_split
```

#### Conversion of effect sizes for gender differences

```{r}
# Read raw data for the meta-analysis of gender differences
raw_gender <- read_tsv(here(data_dir, "04_gender.tsv"), na = "NA")

# Compute relevant effect sizes for the meta-analysis of gender differences
dat_gender <- raw_gender %>%
  # Remove effect sizes from experiments with redundant samples
  filter(!redundant) %>%
  # Add columns
  mutate(

@@

    # Compute standard error of Cohen's d, using harmonic mean of sample sizes
    ni = female_n + male_n,
    nhi = 2 / (1 / female_n + 1 / male_n),
    vi = (df / (df - 2)) * (2 / nhi) * (1 + gi^2 * (nhi / 2)) - (gi^2 / (j^2)),
    sei = sqrt(vi)
  ) %>%
  # Remove experiments that didn't provide any effect size
  filter(!is.na(gi))
```

#### Justification for excluding the Pedrett et al. (2020) paper

```{r}
# Justify exclusion of @pedrett2020 based on outlier mean age
descs_pedrett2020 <- list(age_years = 2.56)
within(descs_pedrett2020, {
  age_months <- age_years * 12
  next_largest_age_months <- max(dat_meta$age_mean) / 30.417
  age <- age_years * 365.25
  z <- (age - mean(dat_meta$age_mean)) / sd(dat_meta$age_mean)
})
```

#### Descriptive information

```{r}
# Extract some descriptive statistics so we can paste them in the main text
(descriptives <- list(
  n_articles = length(unique(dat_meta$article)),
  n_experiments = nrow(dat_meta),
  n_infants = sum(dat_meta$sample_size),
  percent_female = mean(dat_meta$female_percent, na.rm = TRUE),
  min_age_months = as.integer(min(dat_meta$age_min, na.rm = TRUE) / 30.417),
  max_age_months = as.integer(max(dat_meta$age_max, na.rm = TRUE) / 30.417),
  mean_age_weighted = print_days_months(
    sum(dat_meta$age_mean * dat_meta$ni) / (sum(dat_meta$ni)),
    long = TRUE
  ),
  n_experiments_habituation = nrow(filter(dat_meta, task == "Habituation")),
  n_experiments_voe = nrow(filter(dat_meta, task == "VoE"))
))
```

#### Experiments included in the main analysis (Table 1)

```{r}
# Save table of experiments for the meta-analysis of rotation
tab1 <- dat_meta %>%
  mutate(
    age_mean = print_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group,
    `Sample size` = as.integer(sample_size),
    Females = as.integer(round(female_percent * sample_size)),
    `Age ($M$ ± $SD$)` = str_c(age_mean, "±", age_sd, sep = " "),
    Task = as.character(task),
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = str_c(as.integer(stimuli_dimensions), "D")
  ) %>%
  mutate(
    across(.fns = function(x) ifelse(is.na(x), "n/a", x))
  )
